---
title: "Task6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Research & Creative Works Conference 

The Research & Creative Works Conference is held every semester at BYU-Idaho.1 (Links to an external site.) University administrators would like to track student participation in the conference to help them prepare for future semesters. The data have already been collected and attempts have been made to visualize conference trends. You can see the data and charts in this Excel file (https://byuistats.github.io/M335/data/department_data.xlsx). 

A 3D column chart is a poor way to visualize data. Your task is to make a new chart that does a better job of answering the question: How has R&CW attendance changed over time within each department?

```{r cars}
library(readr)
library(ggplot2)
library(tidyverse)


rcw <- read_csv("https://byuistats.github.io/M335/data/rcw.csv", 
col_types = cols(Semester_Date = col_date(format = "%m/%d/%y"), 
Semester = col_factor(levels = c("Winter", "Spring", "Fall"))))
head(rcw)
 
ggplot(data = rcw, mapping = aes(x = Semester_Date, y = Count, 
                     color = Department)) +
  geom_line() +
  geom_point()
```

## Including Plots

You can also embed plots, for example:
glimpse(rcw)

```{r pressure, echo=FALSE}

rcw %>%
  ggplot() +
  geom_line(mapping = aes(x = Semester_Date, y = Count,
                    color = Department)) +
  ggtitle("R&CW attendance overtime") +
        xlab("Semester")+
        ylab("Attendance")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
